Blaming the Typeless: \\ Scalable, Human-Centric Python Localization

### 2018-08-21 paper/main.tex
minor change to motex

\begin{figure}
\begin{lstlisting}
year = int(time.strftime("%Y"))
age = input("Enter your age")
print("You will be twice as old in:")
print(year + age)
\end{lstlisting}
\caption{
\label{fig-motex}
A program with multiple fault localizations (e.g.,
lines 1 and 2).}
\end{figure}

Consider the program in \figref{motex}, adapted from our dataset of
human submissions. The program attempts to carry out some simple arithmetic
based on a given number and the current year. When executed, however, the
program raises an exception on line 4, related to the addition of an
integer variable to a string variable.

>>>>

\begin{figure}
\begin{lstlisting}
year = int(time.strftime("%Y"))
age = input("Enter your age")
print("You will be twice as old in:")
print(year + age)
\end{lstlisting}
\caption{
\label{fig-motex}
A program with multiple fault localizations (lines 1 and 2).}
\end{figure}

One of the key difficulties in localizing type errors, especially for
dynamically-typed programs, is that there are often multiple
logically-valid ways to address a type error~\cite{FIXME} --- only one of
which may be desired by the programmer~\cite{FIXME}.  Consider the program
in \figref{motex}, adapted from our dataset of human submissions. The
program attempts to carry out some simple arithmetic based on a given
number and the current year. When executed, however, the program raises an
exception on line 4, related to the addition of an integer variable to a
string variable.
